---
title: "Demonstration of the `nmahierarchies` package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Demonstration of the `nmahierarchies` package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nmahierarchies)
```

# Required data

We will use the results from a Bayesian random effects network meta-analysis  
(NMA) run on a data set collected by Salliott et al. (2010) to demonstrate the 
functions in this package. This results data consist of 300,000 MCMC samples 
from the joint distribution of the relative effects for each treatment (placebo, 
abatacept, anti-TNF, rituximab, tocilizumab) vs. a reference (placebo), obtained 
from 3 chains (100,000 each). 

Alternatively, samples from the joint distribution of pooled relative effects 
may be simulated using the `ranksampling()` function in the `netmeta` R package.

A data frame consisting of the relative effects vs. a reference treatment should 
only be inputted. The chain index does not needs to be removed.

```{r data}
head(dat_Salliott2010)

# Remove any columns that do not list relative effects of each treatment vs. the
# reference treatment
dat <- dat_Salliott2010[, -1]
head(dat)
```

# Prepare the data

To obtain the data inputs required for each algorithm available in this package,
use the `prep_data()` function.

```{r}
inputs <- prep_data(effects_matrix = dat, 
                    reference = "Placebo", 
                    larger_better = TRUE
)  
```

`prep_data()` creates a list of three R objects: 

* `hierachy_matrix`: a matrix where column headers are ranks and each row 
displays the treatments assigned to each rank for that iteration.

* `effects_matrix`: a matrix where the column headers are treatment names and 
each row displays each treatment’s sampled relative effect for that iteration. 
This should look exactly the same as the data inputted into `prep_data()`.

* `ranking_df`: a data frame of each treatment's ranks and associated 
frequencies.

```{r}
head(inputs$hierarchy_matrix)

head(inputs$effects_matrix)

head(inputs$ranking_df)
```

# Arrangements

To obtain all credible arrangements (e.g., ranked permutations, permutations, 
ranked combinations, and combinations), you may use the `get_arrangements()` 
function. This uses the first algorithm described by Tan et al. (2025).

```{r}
algo1 <- get_arrangements(hierarchy_matrix = inputs$hierarchy_matrix, 
                          threshold = 0.8)
algo1
```

# Partial hierarchies

To obtain all credible partial hierarchies (e.g., A > B > C), you may use the 
`get_partial_hierarchies()` function. This uses the second algorithm described 
by Tan et al. (2025).

```{r}
algo2 <- get_partial_hierarchies(effects_matrix = inputs$effects_matrix, 
                                 mid = 0, 
                                 threshold = 0.8, 
                                 larger_better = TRUE)
algo2
```

# Rankings and high probability density (HPD) sets

To obtain all credible rankings, as well as the high probability density sets, 
for each treatment at a given threshold, you may use the `get_ranks_by_treatment()` 
function. This uses the third algorithm described by Tan et al. (2025).

Note that the rankograms for each treatment may be plotted with overlayed HPD 
sets by setting the `print_plot` argument to TRUE.

```{r}
algo3 <- get_ranks_by_treatment(ranking_df = inputs$ranking_df, 
                                threshold = 0.8, 
                                print_plot = FALSE)
algo3
```

# Check for redundant hierarchies

Some credible hierarchies may be redundant because of other credible hierarchies
in the outputs of algorithms 1 and 2 (e.g., $A > B > C$ is redundant because of 
$(A, B, C)_1^3$), and thus their output is redundant. You may use
`find_redundant_hierarchies()` to detect these redundant hierachies and 
optionally remove them. By default, `find_redundant_hierarchies()` detects 
redundant hierarchies in the order proposed by Tan et al. (2025). The user has 
the option to only check certain hierarchy types, in their preferred order. See 
the help page for more details on 
this.

```{r}
redundant_check <- find_redundant_hierarchies(algo_1 = algo1, 
                                              algo_2 = algo2)
redundant_check

find_redundant_hierarchies(algo_1 = algo1, 
                           algo_2 = algo2, 
                           trim_redundant = TRUE)
```

# All credible hierarchies at once

Alternatively, you may use the `get_all_questions()` to get all credible 
hierarchies that answer binary questions (ranked permutations, permutations, 
ranked combinations, combinations, partial hierarchies, rankings, and HPD sets) 
in one go. Note this function can check if credible hierarchies are redundant 
because of other credible hierarchies in the output, using the default 
settings of `find_redundant_hierarchies()`.

```{r}
all_cred_hier <- get_all_questions(inputs = inputs, 
                                   larger_better = TRUE,
                                   thresholds = c(0.8, 0.8, 0.8), 
                                   mid = 0, 
                                   print_plot = FALSE, 
                                   trim_redundant = FALSE)

all_cred_hier
```
